Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
DSN changes

@@

Moving forward, we seek to solidify the utility metrics by improving upon
second preimage and chosen preimage bounds to validate assumptions about the
utility of collisions. Further, we seek to apply these results to other hash
functions in the same family, such as MD5, SHA-1, and SHA-2. Lastly, it
remains to be seen how this work impacts dissimilar constructions such as
SHA-3 and key derivation functions such as bcrypt and scrypt, and whether
logical cryptanalysis techniques can be applied to these categories of
hash functions as well.

This research and all associated code are open access and open source.
The code is hosted on GitHub at \url{https://github.com/XXXXXXXXXXXXXXXXXX}.
For additional details or to request data associated with the project, please
contact the authors.

@@

The authors would like to thank XXXXX XXXXX for providing hardware for the
project.

>>>>

\linespread{1.05}

@@

While the literature has established a set of known collisions and
some initial algorithms for finding new collisions, the 35 fold
increase in collisions discovered by the methods we have presented in
this paper open a broad range of possible avenues for future work.
Moving forward we plan to solidify the utility metrics by improving upon
second preimage and chosen preimage bounds to validate assumptions about the
utility of collisions. Further, we plan to apply these results to other hash
functions in the same family, such as MD5, SHA-1, and SHA-2 to better
understand if published collisions represent structural weaknesses
which impact the trustworthiness of these broadly used algorithms, or not. Lastly, it
remains to be seen how this work impacts dissimilar hash function constructions such as
SHA-3 and key derivation functions such as bcrypt and scrypt, and whether
logical cryptanalysis techniques can be applied to these categories of
hash functions as well.

In order to help the community build upon or work, and for the
purposes of reproducability and ascertainment of correctness the
research, data, and all associated code are provided on an open access
and open source basis under the GNU General Public License Version 3
\footnote{\url{https://www.gnu.org/licenses/gpl-3.0.en.html}}.
The code itself is hosted on GitHub at \url{https://github.com/XXXXXXXXXXXXXXXXXX}.
For additional details or to request data associated with the project, please
contact the authors.

@@

The authors would like to thank XXXXX XXXXX for providing access to
the hardware used for the
project.
